Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-02 docs/evol.tex
fixes - more on the related work

Our experiment involved the collection of the metric results of the FindBugs
tool. Before and during the experiment, we performed a number of functional
fits on the data coming from the Maven repository,
http://search.maven.org/for reasons that we will describe below.

@@

\begin{table}
\centering
\begin{threeparttable}
\caption{Experiment Entities}
\label{tbl:exp}
\begin{tabular}{l r r}
\hline
Entity & Software Package & Version\\
\hline
Worker & Custom Python Script & 2.7\\
Task Queue & RabbitMQ & 3.0.1 \\
Data Repository & MongoDB & 2.2 \\
Code Repository & Maven Central Repository\tnote{3} & January 2012 \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}

@@

% in a recent paper, Spacco et al.~\cite{SHP06} showed the relation of bugs
% in general, with the size of every version of Sun's {\sc jdk}.

The evolution of software artifacts has also been analyzed to {\it reduce the false
alarms} of the various static analysis tools.
% dimitro: more to come.

>>>>

Our experiment involved the collection of the metric results of the FindBugs
tool. Before and during the experiment, we performed a number of functional
fits on the data coming from the Maven repository, for reasons that we will describe below.

@@

\begin{table}
\centering
\begin{threeparttable}
\caption{Experiment Entities}
\label{tbl:exp}
\begin{tabular}{l r r}
\hline
Entity & Software Package & Version\\
\hline
Worker & Custom Python Script & 2.7\\
Task Queue & RabbitMQ & 3.0.1 \\
Data Repository & MongoDB & 2.2 \\
Code Repository & Maven Central Repository & January 2012 \\
\hline
\end{tabular}
\end{threeparttable}
\end{table}

@@

The evolution of software artifacts has also been analyzed to {\it reduce the false
alarms} of the various static analysis tools. To achieve this, Spacco et
al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
former they tried to pair sets of bugs between versions in order to find
similar patterns. In the latter they computed a signature for every bug. This
signature contained elemnts like the name of the class where the bug was found,
the method and others. Then they searched for similar signatures between
versions. In their research they also studied the evolution of 116 sequential
builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
high priority bugs are fixed over time. To improve the precision of bug
detection, Kim et al.~\cite{KE07b}\cite{KE07} an history-based warning
prioritization algorithm by mining the warning fix experience of three
different projects. The algorithm was based on the following hypothesis: if a
bug that belongs to a specific category is eliminated by a code change, then
this warning category is important. Working towards the same direction Heckman
et al.~\cite{HW09}\cite{HW08} have introduced benchmarks that use specific
correlation algorithms and classification techniques to evaluate alert
prioritization approaches.
